
%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-red}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social informations in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Profile
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Rahil} \headerlastnamestyle{Modi} \\
	\vspace{1mm}
	{\faEnvelope\ rmodi10@gmail.com} | {\faMobile\ (510) 585 - 7576} | {\faMapMarker\ San Jose, CA} | {\faGithub\ rahilmodi} | {\faLinkedin\ rmodi10} |{\faLink\ rahilmodi.github.io}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{
	\begin{tabular}{ l l }
        \textbf{MS} in \textbf{Software Engineering} (GPA: 3.7)\hspace{2cm} & \textbf{Specialization: Enterprise Distribution System} \\ 
    \end{tabular}
    }
	{San Jose State University}
	{San Jose, CA}
	{Jan 2017 - Dec 2018}
	{
	\begin{cvcoursework}
	\vspace{2mm}
	\begin{tabular}{  m{6em}  m{16cm} } 
    \textbf{Coursework : }& {OOP \& Data Structures, Operating System, Enterprise Software Platforms, Enterprise Distributed Systems, Enterprise Application Development, Database Systems, Software Systems Engineering, Cloud Technologies} \\ 
    \end{tabular}
    \end{cvcoursework}
	}
	{}
	\cventry
	{
        \textbf{BE} in \textbf{Electronics and Communication} (GPA: 3.33) 
    }
	{L. D. College of Engineering (GTU)}
	{Ahmedabad, India}
	{Aug 2009 - Jun 2013}
	{}
\end{cventries}

\vspace{-7mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{\textbf{Systems Engineer}}
	{Tata Consultancy Services (Nissan Motors Co. Ltd.)}
	{Pune, India}
	{Mar 2014 – Dec 2016}
	{
	\vspace{1mm}
	\begin{cvresponsiblties}
		\item {Designed \& implemented 10+ features and enhanced existing functionalities of Automotive Diagnostic Software in C++.}
		\item {Resolved 20+ issues by static-code \& log analysis and fixed memory leaks leading to increase in performance.}
		\item {Developed a POC of next-generation tool using RESTful services based on SOA in Java.}
		\item {Assisted as a mentor in on-boarding process and served as a release and build SPOC.}
	\end{cvresponsiblties}
	\vspace{-2mm}
	}
	\cventry
	{\textbf{Software Engineer Intern}}
	{Innoventaa Technocrats}
	{Ahmedabad, India}
	{Aug 2013 – Jan 2014}
	{
	\vspace{1mm}
	\begin{cvresponsiblties}
		\item {Developed an eCommerce prototype with features like product, purchase, user management.}
		\item {Technologies used: Java, J2EE, JSP, servlet, hibernate, JDBC, MySQL}
		\end{cvresponsiblties}
	}
\end{cventries}
\vspace{-5.5mm}
\cvsection{Skills}
\vspace{-4mm}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.25}{\begin{tabular}{ l l }
	    \vspace{0.4mm}
		Languages:  & {\skill{ Java, JavaScript(ES6), C++, Python}} \\
		\vspace{0.4mm}
		Back-End Technologies:  & {\skill{ Spring, Hibernate, J2EE, flask, Node.js, RabbitMQ, MVC, AWS Lambda, Kafka, Zookeeper}} \\
		\vspace{0.4mm}
		Front-End Technologies:  & {\skill{ HTML5, CSS3, Bootstrap, AngularJS, React, Redux}} \\
		\vspace{0.4mm}
		Tools/Libraries:  & {\skill{ Git, SVN, socket.io, Maven,  eclipse, IntelliJ, JUnit, OpenCV, Docker}} \\
		\vspace{0.4mm}
		Databases:  & {\skill{ MySQL, SQLite, redis, MongoDB, cassandra, DynamoDB}} \\
		\vspace{0.4mm}
		Design \& Development:  & {\skill{ Agile, Scrum, Design Patterns, OAuth2, REST, SOAP, GraphQL}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}
\vspace{-11mm}
\cvsection{Projects}
\begin{cventries}
	\cvprojectentry
	{
	\begin{cvitems}
    	\item {A highly scalable, fault-tolerant and distributed service to shorten URLs developed in Java/Spring Boot. }
    	\item {Achieved high coordination and availability using zookeeper and faster response time using redis caching.}
	\end{cvitems}
	}
	{TinyURL}
	{Spring Boot/Security, Zookeeper, Cassandra, redis, OAuth2}
	\cvprojectentry
	{
	\begin{cvitems}
    	\item {A 3-tier web application to post or volunteer for a work.}
    	\item {Key features : real-time \& email notification, authentication using OAuth2 and badge sharing on Facebook.}
	\end{cvitems}
	}
	{Help Other}
	{MEAN, socket.io, passport.js, heroku}
	\cvprojectentry
	{
	\begin{cvitems}
    	\item {A server-less pizza ordering system based on AWS lamda and REST APIs, developed in Python using API Gateway and data persisted in DynamoDB.}
	\end{cvitems}
	}
	{Pizza Ordering System}
	{AWS lambda, DynamoDB, API Gateway, Python}
	\cvprojectentry
	{
	\begin{cvitems}
    	\item {Built a single page application for attendance and immigration system based on face recognition.}
    	\item {Dockerized application developed in python-flask using OpenCV and cloud based data persistence.}
	\end{cvitems}
	}
	{Face Recognition web app}
	{Python, flask, OpenCV, mLab, Angular, Docker, AWS EC2}
	\cvprojectentry
	{
	\begin{cvitems}
    	\item {Developed a real-time order status analysis system to track \& visualize changes in orders status every 5 seconds.}
    	\item {Accomplished high scalability using multi-broker Kafka with spark streaming and zeppelin & D3.js for visualization.}
	\end{cvitems}
	}
	{Real-time Order Status Analysis}
	{Java, Kafka, Spark, Zeppelin, D3.js}
    \vspace{-2mm}
\end{cventries}
\vspace{-3mm}
\cvsection{Award}
\begin{cvhonors}
	\cvhonor
	{TCS On The Spot}
	{for outstanding performance and bug free feature roll out.}
	{Pune, India}
	{Mar 2016}
\end{cvhonors}
\ 
\end{document}